### 2008-12-19 talk/ecoop2009/jitgen.tex
remove the jitstrategy section and integrate its contents into the introduction.
some fixes
Move the \labels to their proper location. Otherwise the references to them are bogus.
kill a now-unnecessary section

\begin{figure}[h]
\label{fig:tlc-main}
\begin{center}
\input{tlc-simplified.py}
\caption{The main loop of the TLC interpreter, written in RPython}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\label{fig:tlc-folded}
\begin{center}
\input{tlc-folded.py}
\caption{The residual code of the TLC main loop with respect to the
\lstinline{abs} function }
\end{center}
\end{figure}

@@

\subsection{Partial Evaluation in PyPy}

PyPy contains a framework for generating just-in-time compilers using
off-line partial evaluation.  As such, there are three distinct phases:

\begin{itemize}
\item \emph{Translation time:} during the normal translation of an RPython
program, say the TLC interpreter, we perform binding-time analysis on the
interpreter.  This produces a generating extension, which is linked with the
rest of the program. \cfbolz{XXX not quite right}

\item \emph{Compile time:} during the execution of the program, when a new
bytecode is about to be interpreted, the generating extension is invoked
instead.  As the generating extension is a compiler, all the computations it
performs are called compile-time computations.  Its sole effect is to produce
residual code.

\item \emph{Run time:} the normal execution of the program (which includes the
time spent running the residual code created by the generating extension).
\end{itemize}

Translation time is a purely off-line phase; compile time and run time are
actually highly interleaved during the execution of the program.

\subsection{Binding Time Analysis}

At translation time, PyPy performs binding-time analysis of the source
RPython program after it has been turned to low-level graphs, i.e. at
the level at which operations manipulate pointer-and-structure-like
objects.

@@

\subsection{Hints}

@@

Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation.  See the Promotion section XXX ref for a
complete discussion of promotion.

>>>>

\begin{figure}[h]
\begin{center}
\input{tlc-simplified.py}
\caption{The main loop of the TLC interpreter, written in RPython}
\label{fig:tlc-main}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\input{tlc-folded.py}
\caption{The residual code of the TLC main loop with respect to the
\lstinline{abs} function }
\label{fig:tlc-folded}
\end{center}
\end{figure}

@@

\subsection{Binding Time Analysis in PyPy}

XXX need better transition text from last section
At translation time, PyPy performs binding-time analysis of the source
RPython program after it has been turned to low-level graphs, i.e. at
the level at which operations manipulate pointer-and-structure-like
objects.

@@

\subsection{Hints}
\label{sec:hints}

@@

Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation.  See Section \ref{sec:promotion} for a
complete discussion of promotion.
